Manuscript 1: Adult Health Effects

### 2020-11-23 paperone_adult_health.Rmd
Updates to analysis for child health paper.

totalpop <- data.frame(table(mydata_complete$current_zip))
colnames(totalpop) <- c("current_zip", "pop")

@@

table_predictors <- CreateTableOne(vars=c("age", "gender", "collapseeduc", "public_benefits", "collapsemarital", "number_children", "years_cityflint", "confidants2"), strata = "collapserace", data=mydata_complete, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE))

table_outcomes <- CreateTableOne(vars=c("num_time_notice", "blood_test_after_april_2014", "elevated_lead_after_april_2014", "rashes_after_april_2014", "hairloss_after_april_2014", "nausea_after_april_2014", "irritable_after_april_2014", "overall_collapse", "ptsd_bin", "phq_bin"), strata = "collapserace", data=mydata_complete, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE))

@@

table_predictors_notstrat <- CreateTableOne(vars=c("age", "gender", "collapseeduc", "public_benefits", "collapsemarital", "number_children", "years_cityflint", "confidants2"), data=mydata_complete, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE))

table_outcomes_notstrat <- CreateTableOne(vars=c("num_time_notice", "blood_test_after_april_2014", "elevated_lead_after_april_2014", "rashes_after_april_2014", "hairloss_after_april_2014", "nausea_after_april_2014", "irritable_after_april_2014", "overall_collapse", "ptsd_bin", "phq_bin"), data=mydata_complete, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE))

>>>>

totalpop <- data.frame(table(mydata$current_zip))
colnames(totalpop) <- c("current_zip", "pop")

@@

table_predictors <- CreateTableOne(vars=c("age", "gender", "collapseeduc", "public_benefits", "collapsemarital", "number_children", "years_cityflint", "confidants2"), strata = "collapserace", data=mydata, includeNA = TRUE, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE))

table_outcomes <- CreateTableOne(vars=c("num_time_notice", "blood_test_after_april_2014", "elevated_lead_after_april_2014", "rashes_after_april_2014", "hairloss_after_april_2014", "nausea_after_april_2014", "irritable_after_april_2014", "overall_collapse", "ptsd_bin", "phq_bin"), strata = "collapserace", data=mydata, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA = TRUE)

@@

table_predictors_notstrat <- CreateTableOne(vars=c("age", "gender", "collapseeduc", "public_benefits", "collapsemarital", "number_children", "years_cityflint", "confidants2"), data=mydata, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA=TRUE)

table_outcomes_notstrat <- CreateTableOne(vars=c("num_time_notice", "blood_test_after_april_2014", "elevated_lead_after_april_2014", "rashes_after_april_2014", "hairloss_after_april_2014", "nausea_after_april_2014", "irritable_after_april_2014", "overall_collapse", "ptsd_bin", "phq_bin"), data=mydata, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA=TRUE)
